---
title: "C.diff Pet’s Study"
author: "Jeffrey Berinstein"
date: "11/15/2018"
output: word_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(error = TRUE)
library(shiny)
library(rmarkdown)
library("knitr")
devtools::session_info()
```

  

## Figure 1: Flow Diagram 

n = 'r nrow(cdi1)' were contacted by letter or phone call
This was made up of 'r cdi_total_by_cdi_status' where 0 = CDI- and 1 = CDI+

n= 'r nrow(mtable1)' answered the survey
This was made up of 'r mtable %>% sort_by(cdi_status) %>% summarize(total=n()))' where 0 = CDI- and 1 = CDI+

3 patients where removed due to incomplete data
6 patients where removed due to duplicates

'r nrow(cdi1)- nrow(mtable1)' where removed due to lack of response

'r nrow(mtable3)' was removed due to being included as a negative control based on our institutional EMR, however discussion with patient reveiled prior history of CDI

'r (nrow(cdi1)- nrow(mtable1))- nrow(mtable3)' is the number of patients remaining


'r svy_com_status_final' final numbers where 0 = CDI- and 1 = CDI+


##Table One

```{r tables}
library(tableone)
library(magrittr)

listVars <- c("gender", "age", "race", "antibiotics3mo","ppi","h2ra", "adl_total") 
catVars <- c("gender", "race", "antibiotics3mo","ppi","h2ra", "adl_total")
table2 <- CreateTableOne(listVars, mtable4, catVars, strata = c("cdi"))

table2 

```

---
```{r}

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Table 1

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
