---
title: "C.diff Pet’s Study"
author: "Jeffrey Berinstein"
date: "11/15/2018"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r, include = FALSE}
knitr::opts_chunk$set(error = TRUE)
library(shiny)
library(rmarkdown)
library("knitr")
devtools::session_info()
```

  

## Figure 1: Flow Diagram 

896 patients called or sent letters (461 CDI neg, 435 CDI pos)
444 Remaining (446 removed due to not answering)
414 remaining (30 removed due to +PMH of CDI and being called as a neg control)
414 (206 CDI- and 208 CDI+)
411 after 3 removed for being <18 (2 CDI positive and 1 CDI neg)
410 after 1 remove for being >90 (1 CDI positive male)
Final numbers: 205 CDI negative and 205 CDI positive patients included in this study


##Table One

```{r table, echo = FALSE}
library(tableone)
library(magrittr)

listVars <- c("gender", "age", "race", "antibiotics3mo","ppi","h2ra", "adl_total") 
catVars <- c("gender", "race", "antibiotics3mo","ppi","h2ra", "adl_total")
table1 <- CreateTableOne(listVars, mtable5, catVars, strata = c("cdi_status"))

table1

```


#Leaps plot for varaible selection

```{r leaps plot, message = FALSE}

leaps=regsubsets(cdi_status~ gender + age + race + restaurant3 + dessert3 + meat3 + salad3+redwine3 +dairy +
                   vitamin + probiotic + antibiotics3mo + ppi +h2ra + acid_blocker_yes + health_care + hospital3 +
                   hc_facility3 + adl_total + dog + dog_outside + cat + cat_outside, data=clean_table_strata, nbest=10)

leaps=regsubsets(cdi_status~ hc_facility3 + adl_total + dog + dog_outside + cat + cat_outside, data=clean_table_strata, nbest=10)

plot(leaps, scale="adjr2")


```


#Linear Model

```{r linear regression model, message=FALSE}


lm1<-lm(cdi_status ~ hc_facility3 + age +probiotic + hospital3 + adl_total +
  dog:dog_outside, clean_table_strata1)

summary(lm1)

```

#Conditional Model


```{r conditional regression, message=FALSE}
res.clogit3.int <- survival::clogit(cdi_status ~ hc_facility3 + probiotic + hospital3 + adl_total +
                                      dog:dog_outside + strata(stratum), clean_table_strata1)

summary(res.clogit3.int)

```
